## `r paste(column_name)` Histogram

:::::::::::::: {.columns}
::: {.column}

This slide is describing in details the column `r paste(column_name)`.

- Minimum value `r round(min(df[column_name], na.rm=T))` kW
- Maximum value `r round(max(df[column_name], na.rm=T))` kW

:::
::: {.column}
```{r , out.width = "100%", out.height = "100%", dpi = 200}

ggplot(df) + 
geom_histogram(aes(value), color = "#a5d39f",fill= "#a5d39f", show.legend = F) +
  theme(
    panel.background = element_rect(fill = "#242424"), # bg of the panel
    axis.title.x = element_text(color = "white"),
    axis.title.y = element_text(color = "white"),
    axis.text.x = element_text(color = "white"),
    axis.text.y = element_text(color = "white"),
    axis.line.x = element_line(color = "white"),
     axis.line.y = element_line(color = "white"),
    plot.background = element_rect(fill = "#242424", color = NA), # bg of the plot
    panel.grid.major = element_blank(), # get rid of major grid
    panel.grid.minor = element_blank(), # get rid of minor grid
    legend.background = element_rect(fill = "#242424"), # get rid of legend bg
    legend.box.background = element_rect(fill = "#242424") # get rid of legend panel bg
  )

# 
# ggplot(df) + 
#   geom_line(aes(x = time, y = value), color = "#a5d39f", show.legend = F) +
#   theme(
#     panel.background = element_rect(fill = "#242424"), # bg of the panel
#     axis.title.x = element_text(color = "white"),
#     axis.title.y = element_text(color = "white"),
#     axis.text.x = element_text(color = "white"),
#     axis.text.y = element_text(color = "white"),
#     axis.line.x = element_line(color = "white"),
#      axis.line.y = element_line(color = "white"),
#     plot.background = element_rect(fill = "#242424", color = NA), # bg of the plot
#     panel.grid.major = element_blank(), # get rid of major grid
#     panel.grid.minor = element_blank(), # get rid of minor grid
#     legend.background = element_rect(fill = "#242424"), # get rid of legend bg
#     legend.box.background = element_rect(fill = "#242424") # get rid of legend panel bg
#   )


```
:::
::::::::::::::

## `r paste(column_name)` Line Plot

:::::::::::::: {.columns}
::: {.column}

This slide is describing in details the column `r paste(column_name)`.

- Minimum value `r round(min(df[column_name], na.rm=T))` kW
- Maximum value `r round(max(df[column_name], na.rm=T))` kW

:::
::: {.column}
```{r , out.width = "100%", out.height = "100%", dpi = 200}


ggplot(df) +
  geom_line(aes(x = time, y = value), color = "#a5d39f", show.legend = F) +
  theme(
    panel.background = element_rect(fill = "#242424"), # bg of the panel
    axis.title.x = element_text(color = "white"),
    axis.title.y = element_text(color = "white"),
    axis.text.x = element_text(color = "white"),
    axis.text.y = element_text(color = "white"),
    axis.line.x = element_line(color = "white"),
     axis.line.y = element_line(color = "white"),
    plot.background = element_rect(fill = "#242424", color = NA), # bg of the plot
    panel.grid.major = element_blank(), # get rid of major grid
    panel.grid.minor = element_blank(), # get rid of minor grid
    legend.background = element_rect(fill = "#242424"), # get rid of legend bg
    legend.box.background = element_rect(fill = "#242424") # get rid of legend panel bg
  )


```
:::
::::::::::::::